\documentclass[12pt,a4paper]{article}

% we use this for strike through text that is going to be removed in the final report
\usepackage{soul}
\renewcommand{\baselinestretch}{1.15}

\newcommand{\bigsize}{\fontsize{35pt}{20pt}\selectfont}
\begin{document}
\begin{titlepage}
    \title{INFO3406 Project Stage 1}
    \author{Zhu Linzi\\
            \and
            Zhou Nic
    }
    \date{September 2018}
    \maketitle
\end{titlepage}

    \pagebreak
    \tableofcontents
    \pagebreak

    \section{Section 1: Problem}
    The results of the 2016 Presidential elections came as surprise to the whole world. The candidate Hillary Clinton \
    was ahead in the polls throughout the whole election cycle. Yet when November 8 came the victor was none other than\
    Donald J. Trump. The problem that we are trying to identify is where everyone went wrong in their predictions.
    \newline \newline
    The questions we will be answering in Stage 2 are:

    \begin{enumerate}
        \item What are the factors that will lead to victories in US elections?
        \item How accurate is polling data in terms of predicting the winner of an election?
        \item How can extraordinary events affect a candidate's chances of winning?
        \item Which candidates will most likely win in the 2018 US Midterm elections?
    \end{enumerate}

    \section{Section 2: Approach}
    In this section we will describe the approach we will be taking to solving the problem and any requirements. This is our plan for stage 2.

    \section{Section 3: Data}

    The data was acquired from \st{https://github.com/mdeff/fma} https://www.kaggle.com/.
    \newline \newline
    The tools we used were:

    \begin{itemize}
        \item python
        \item weka
        \item SPSS
    \end{itemize}
    \appendix
    \section{}
    Not really sure what though. Probably an appendix.
\end{document}
